\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Note on sim alpha channel

The second image viewed after the initial tutorial image is already a survey
image, in order to get the volunteers engaged in the real task as quickly as
possible. However, training then continues, beyond the first image tutorial,
through ``training subjects'' inserted randomly into the stream.  These
training subjects are either simulated lenses (known as ``sims''), or survey
images that were expert-classified and found not to contain any lens
candidates (these images are known as ``duds''). The tutorial explains that
the volunteers  will be shown such training images. They are also informed
that they will receive instant feedback about their performance after
classifying (blindly) any of these training subjects. Indeed, after a volunteer
finishes marking a training subject, a pop-up
message is generated, containing either congratulations for a successful
classification (for example, ``Well done! You spotted a simulated lens,'' as
in \Fref{fig:screenshot}) or feedback for an unsuccessful one (for
example, ``There is no gravitational lens in this field!'').

@@

The instant feedback provides real-time educational responses to the volunteers
as they start classifying; as well as this dynamic system, \SW provides a static
reference work for volunteers to consult when in doubt about how to perform the
task. This ``Spotter's Guide'' is a set of webpages showing example lenses, both
real and simulated, and also some common false positives, drawn from the pool of
survey images. The false positives were identified during the selection of the
``dud'' training images (previous section). For easy reference, the lenses are
divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
``cluster lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button on
the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

Most of the text of the Spotter's Guide focuses on what kinds of image features
gravitational lenses do or don't produce;
the website ``Science page'' contains a very brief introduction to how
gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
The FAQ also contains answers to frequently asked questions about the interface
and the task set.

@@

The \StageOne training set was chosen to be quite clear cut, in order to err on
the side of inclusivity, and so ensure high completeness. When defining the
training duds we discarded anything that could be considered a lens candidate
(see \Sref{sec:design:training:guide}): this meant that objects that look
similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
blue stars and so on, were specifically excluded from the training set, and
therefore we expect some of those types of object to appear in the \StageOne
candidate list. As described above, the training sims for \StageOne were also
selected to be relatively straightforward to spot.

@@

The design of a \StageOne classification task, and its training set, should
lead to sample of lens candidates that has high completeness but may have low
purity. To refine this sample to higher purity, we need to reject more
non-lenses, which means providing the volunteers with a more realistic and
challenging training set as they re-classify it. The more demanding \StageTwo
training set was generated as follows. The \StageTwo duds were selected
from a small random subset of the \StageOne candidates (i.e., the \StageTwo duds
were expert-defined \StageOne false positive detections), while the \StageTwo
sims were chosen to be a subset of the \StageOne sims, none of which were deemed
``obvious'' by the same expert classifiers. This meant that the \StageTwo sims
had fainter and less well-separated image features than in the \StageOne
training set.  Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds} show some example images from the resulting
\StageTwo training set.

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

The second image viewed after the initial tutorial image is already a survey
image, in order to get the volunteers engaged in the real task as quickly as
possible. However, training then continues, beyond the first image tutorial,
through ``training subjects'' inserted randomly into the stream.  These
training subjects are either simulated lenses (known as ``sims''), or survey
images that were expert-classified and found not to contain any lens
candidates (these images are known as ``duds''). The tutorial explains that
the volunteers  will be shown such training images. They are also informed
that they will receive instant feedback about their performance after
classifying (blindly) any of these training subjects. Indeed, after a volunteer
finishes marking a training subject, a pop-up
message is generated, containing either congratulations for a successful
classification (for example, ``Well done! You spotted a simulated lens,'' as
in \Fref{fig:screenshot}) or feedback for an unsuccessful one (for
example, ``There is no gravitational lens in this field!''). A successful
classification of a simulated lens requires a marker to be placed fairly
precisely on the lensed features, so as to avoid misinforming the classifier.
The pixels in the lensed features are flagged via a mask contained in the
PNG image transparency ``alpha'' channel. (The mask is not visible in the image.)

@@

The instant feedback provides real-time educational responses to the volunteers
as they start classifying; as well as this dynamic system, \SW provides a static
reference work for volunteers to consult when in doubt about how to perform the
task. This ``Spotter's Guide'' is a set of webpages showing example lenses, both
real and simulated, and also some common false positives, drawn from the pool of
survey images. The false positives were identified during the selection of the
``dud'' training images (previous section). For easy reference, the lenses are
divided by type (for example, ``Lensed Galaxies,'' ``Lensed Quasars'' and
``Cluster Lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button on
the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

Most of the text of the Spotter's Guide focuses on the kinds of features that
gravitational lenses do or don't produce. To complement this,
the website ``Science page'' contains a very brief introduction to how
gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
The FAQ also contains answers to frequently asked questions about the interface
and the task set.

@@

The \StageOne training set was chosen to be quite clear cut, in order to err on
the side of high completeness. When defining the
training duds, we discarded anything that could be considered a lens candidate
(see \Sref{sec:design:training:guide}). This meant that objects that look
similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
blue stars and so on, were specifically excluded from the training set, and
therefore we expect some of those types of object to appear in the \StageOne
candidate list. As described above, the training sims for \StageOne were also
selected to be relatively straightforward to spot.

@@

The design of a \StageOne classification task, and its training set, should
lead to a sample of lens candidates that has high completeness but may have low
purity. To refine this sample to higher purity, we need to reject more
non-lenses, which means providing the volunteers with a more realistic and
challenging training set as they re-classify it. The more demanding \StageTwo
training set was generated as follows. The \StageTwo duds were selected
from a small random subset of the \StageOne candidates (i.e., the \StageTwo duds
were expert-defined \StageOne false positive detections), while the \StageTwo
sims were chosen to be a subset of the \StageOne sims, none of which were deemed
``obvious'' by the same expert classifiers. This meant that the \StageTwo sims
had fainter and less well-separated image features than in the \StageOne
training set.  Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds} show some example images from the resulting
\StageTwo training set.

@@

\bibliographystyle{apj}
\bibliography{references_system}
